### 2023-06-20 paper/sec-dis-pseudodata.tex
Update sec-dis-pseudodata.tex

@@

\begin{figure}[h]
    \centering
\includegraphics[width=1\textwidth]{plots/Nevent_FASERv2_14.pdf}
    \caption{Event rate per bin for muon neutrinos at FASER$\nu$2. Bins are denoted by dashed grid, and the red dot indicates the weighted average of $x,Q^2$ points in each bin. The total number of muon neutrino events calculated is $\approx2.6\times 10^5$. Note that bins were chosen somewhat arbitrarily, and can be iterated to improve PDF fits }
    \label{fig:fasernu2_muon}
\end{figure}

>>>>

Table~\ref{tab:integrated_rates} summarises the predicted integrated event yields for the five detectors considered
  in the present analysis, separated into electron neutrinos and antineutrinos
  and muon neutrinos and antineutrinos.
  %
  These event yields are computed from Eq.~(\ref{eq:event_yields}) with the only
  restriction that the momentum transfer and the final-state invariant mass should be restricted
  to the DIS region, $Q^2 \ge 2$ GeV$^2$ and $W^2 \ge 12.5$ GeV$^2$.
  %
  As discussed above, for FASER$\nu$ and SND@LHC we assume the integrated luminosity to
  be that of Run III while for the FPF experiments we assume the full HL-LHC
  luminosity (3 ab$^{-1}$).
  %
   The numbers in parenthesis indicate the event rates corresponding to charm
  production for those experiments with heavy flavour tagging capabilities.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-----------------------------------------------------------------
\begin{table}[t]
  \centering
  \small
  \renewcommand{\arraystretch}{1.60}
\begin{tabularx}{\textwidth}{X|c|c|c|c|c|c}
\toprule
Detector & $\quad$ $N_{\nu_e}$ $\quad$ &$\quad$ $N_{\bar{\nu}_e}$$\quad$   &   $N_{\nu_e} + N_{\bar{\nu}_e}$ &
$\quad$$N_{\nu_\mu}$ $\quad$ & $\quad$ $N_{\bar{\nu}_\mu}$ $\quad$  &   $N_{\nu_\mu} + N_{\bar{\nu}_\mu}$ \\
\midrule
FASER$\nu$  &    &    &   &   &    &    \\
SND@LHC  &    &    &   &   &    &    \\
\midrule
FASER$\nu$2  &    &    &   &   &    &    \\
AdvSND~(far)  &    &    &   &   &    &    \\
FLArE &    &    &   &   &    &    \\
  \bottomrule
\end{tabularx}
\vspace{0.2cm}
\caption{\small The predicted integrated event yields for the five detectors considered
  in the present analysis, separated into electron neutrinos and antineutrinos
  and muon neutrinos and antineutrinos.
  %
  These event yields are computed from Eq.~(\ref{eq:event_yields}) with the only
  restriction that the momentum transfer and the final-state invariant mass be restricted
  to the DIS region, $Q^2 \ge 2$ GeV$^2$ and $W^2 \ge 12.5$ GeV$^2$.
  %
  The numbers in parenthesis indicate the event rates corresponding to charm
  production.
  \label{tab:integrated_rates}
}
\end{table}
%-----------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Eq.~(\ref{eq:event_yields}) can be generalised to charm-production events, with
the only difference beings that now the neutrino scattering cross-section is restricted
to those processes leading to final-state charm quarks.
%
Assuming that charm quarks can be directly tagged by the detector one has
\be
\label{eq:event_yields_charm}
  N_{\rm ev,c}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma^{\nu N \to \ell + c+X}(x,Q^2,E_{\nu})}{dxdQ^2}\right) dQ^2 dx dE_{\nu} \, 
  \ee
  with the charm production cross-sections being discussed in~\cite{Faura:2020oom}
  and references therein.
  %
  Detectors without charm-tagging capabilities can still be sensitive to charm production via
  the semileptonic decays of the $D$-mesons, resulting in the characteristic
  dimuon topology, where
  \be
 N_{\rm ev,2\mu}^{(i)} \approx N_{\rm ev,c}^{(i)} \times \mathcal{B}\lp c \to D \to \mu + X\rp \, ,
 \ee
 with $\mathcal{B}$ a numerical factor that accounts for charm hadronisation and the
 resulting semileptonic decay to a muon.
 %
 Given that $\mathcal{B}\sim 0.1$, being able to tag directly charm quarks increases the event yields
 of charm production events by a factor 10 as compared to reconstructing the dimuon final state.
 %
 Here we neglect finite acceptance effects, which can only be properly estimated by means
 of a full detector simulation.

%-----------------------------------------------------------------------
\begin{figure}[t]
    \centering
\includegraphics[width=1\textwidth]{plots/Nevent_FASERv2_14.pdf}
    \caption{Event rate per bin for muon neutrinos at FASER$\nu$2. Bins are denoted by dashed grid, and the red dot indicates the weighted average of $x,Q^2$ points in each bin. The total number of muon neutrino events calculated is $\approx2.6\times 10^5$. Note that bins were chosen somewhat arbitrarily, and can be iterated to improve PDF fits }
    \label{fig:fasernu2_muon}
\end{figure}
%-----------------------------------------------------------------------

@@

charm production
